DeepSphere: Efficient spherical Convolutional Neural Network with HEALPix sampling for cosmological applications

### 2018-12-05 rebuttal.tex

- It should be "which makes it computationally efficient" instead of "what". (It's possibly "that" and not "which", but I'm never sure which ;))
\end{mdframed}
\todo{Answer}

\begin{mdframed}[style=comment] 
A straightforward way to impose locality in the original domain is to impose smoothness in the spectral domain, by Heisenberg’s uncertainty principle.

- What do you mean by "by Heisenberg’s uncertainty principle." That seemed to come out of nowhere. This needs explaining further.
\end{mdframed}
\todo{Answer}

\begin{mdframed}[style=comment] 
All the above methods cannot be easily accelerated when the data lies on a part of the sphere only.

- You mention your method as part of the "above methods", but then you go on to say that using graphs does allow you to accelerate the method when data is only on part of the sphere.
\end{mdframed}
\todo{Answer}

\begin{mdframed}[style=comment] 
By interwinding graph convolutional layers and recurrent layers [65], they can for example model structured time series such as traffic on road networks [66], or recursively complete matrices for recommendation [67].

- I'm not sure what interwinding is, I guess you mean by making GC recurrent, or do you mean using GC and then RL separately? Either way there should be commas around "for example".
\end{mdframed}
\todo{Answer}

\begin{mdframed}[style=comment] 
To prevent the cosmological models to be distinguished by their power spectra alone, the maps have been smoothed with a Gaussian kernel of radius 3 arcmins to remove high frequencies ($\ell$ > 1000).

- This should be "To prevent the cosmological models from being distinguished by their power spectra alone the maps have been smoothed with a Gaussian kernel of radius 3 arcmins to remove high frequencies ($\ell$ > 1000).
\end{mdframed}
\todo{Answer}

\begin{mdframed}[style=comment] 
The two sets of maps were created using the standard cosmological model with two sets of cosmological parameters.

- Can you add that you are going to describe the details more thoroughly in section 4.1.
\end{mdframed}
\todo{Answer}

\begin{mdframed}[style=comment] 
Implementation of full cosmological inference requires, however, many more simulations, building the likelihood function, and several other auxiliary tasks.

- Unless you have a cheap neural network based likelihood-free method ;)
\end{mdframed}
\todo{Answer}

\begin{mdframed}[style=comment] 
For each class, we generate 30 simulations.

- Just mention that there are two classes again, to make it clear that "class" means "cosmology".
\end{mdframed}
\todo{Answer}

\begin{mdframed}[style=comment] 
That is a data augmentation scheme, as it creates more training examples than we have simulations.

- I think that you should introduce the Gaussian noise paragraph by stating that you perform data augmentation via the addition of randomly drawn Gaussian noise, rather than talking about the random noise first and then explaining that the reason is for data augmentation. ML specialists in particular will be happier with the addition of noise for DA (as will cosmologists I think).
\end{mdframed}
\todo{Answer}

\begin{mdframed}[style=comment] 
Probabilities are computed by the SM layer.

- As explained above, these are not probabilities, they are class predictions from the network.
\end{mdframed}
\todo{Answer}

\begin{mdframed}[style=comment] 
As less pixels are available to make a decision about a sample, the algorithms have access to less information and make more mistakes.

- Should be "As fewer pixels...". Also, "makes more mistakes" kind of anthropomorphises the network too much. Perhaps "have access to less information and thus cannot classify as well".
\end{mdframed}
\todo{Answer}

\begin{mdframed}[style=comment] 
This standard deviation has the property to keep the energy of the signal more or less constant across layers

- Should be "of keeping" instead of "to keep". "This standard deviation has the property of keeping the energy of the signal more or less constant across layers"
\end{mdframed}
\todo{Answer}

\begin{mdframed}[style=comment] 
We derived this rule from the Chebyshev polynomial equations and some empirical experiments.

- This is a bit loose, can you explain further and add a citation if you didn't do the experiments yourself?
\end{mdframed}
\todo{Answer}

\begin{mdframed}[style=comment] 
Figure 10: Random selection of 24 learned filters from the fifth spherical convolutional layer L5. Top: section. Bottom: gnomonic projection.

- There is not enough information in this caption. Can you explain that there is some obvious peak structure. I think a colourbar on the gnomonic projection would be useful too.
\end{mdframed}
\todo{Answer}

\begin{mdframed}[style=comment] 
The fact that a graph representation of the disretised sphere enables an efficient convolution relaxes the iso-latitude constraint on the design of sampling schemes who aim to enable fast convolutions.

- It should be "discretised" and also "who" should be "which" (or "that", I'm not actually sure myself)
\end{mdframed}
\todo{Answer}

\begin{mdframed}[style=comment] 
In the long term, it might enable researchers to consider sampling schemes with different trade-offs, or remove the need for schemes and interpolation altogether and simply consider the positions at which measures were taken.

- What is "it" here? DeepSphere or graph networks or something else?
\end{mdframed}
\todo{Answer}

\begin{mdframed}[style=comment] 
We believe that it might be the case for a different construction of the graph (fully connected) and that a proof could be built on top of the work of [33]. That is, however, out of the scope of this contribution.

- What makes you believe this? If you don't want to mention it in this paper, please don't speculate a "belief". I might just be reading the sentence incorrectly, but it makes me a little uncomfortable when there is no evidence backing that up. If you have some evidence then it's worth presenting it.
\end{mdframed}
\todo{Answer}

\begin{mdframed}[style=comment] 
In this case, the graph setting used through this contribution correspond to assume reflective border conditions.

- It should be "assumed". "In this case, the graph setting used through this contribution correspond to assumed reflective border conditions."
\end{mdframed}
\todo{Answer}

\begin{mdframed}[style=comment] 
Nevertheless, dealing working with a subpart of the sphere, its border slightly affects the convolution.

- There is a superfluous word (dealing/working). I think this would read better as "Nevertheless, when working with only a part of the sphere, the border slightly affects the convolution."
\end{mdframed}
\todo{Answer}

\begin{mdframed}[style=comment] 
These border effects can, however, be mitigated by padding with zeros a small area around the part of interest.

- Are they really mitigated? Surely there are still effects but you are happy with the level?
\end{mdframed}
\todo{Answer}

\begin{mdframed}[style=comment] 
Furthermore, this result is another sign that the constructed graph is able to capture the spherical structure of the HEALPix sampling.

- What does "this" refer to?
\end{mdframed}
\todo{Answer}

\begin{mdframed}[style=comment] 
In a neural network setting, the fact that the graph convolution is not exactly equivariant to rotation is probably compensated by the fact that convolution kernels are learned.

- I think is might be another one of the most important points in the paper which allows you to justify why not being exact (like a spherical harmonic transform) is acceptable. If I were you I'd move this into the main body of the paper.
\end{mdframed}
\todo{Answer}

\begin{mdframed}[style=comment] 
We then plot the result with a gnomonic projection.

- Can you add in Figure C.16 here. "We then plot the result with a gnomonic projection, as shown in Figure C.16". Also, why do you choose a gnomonic projection? In fact, with plots C.16 and C.17 I would make them a single plot (as in Figure. 10),
\end{mdframed}
\todo{Answer}

\begin{mdframed}[style=comment] 
We plot the section of the convoluted Kroneker.

- It should be "convolved" and probably stick with "Kroneker $\delta$". Also, why are you plotting this? What does it show? Can you go into a bit more detail?
\end{mdframed}
\todo{Answer}

\begin{mdframed}[style=comment] 
The error clearly converged and adding more samples will not help.

- I think this should be "converges such that" rather than "converged and". And rather than "help" I think "improve convergence further" is more descriptive.
\end{mdframed}
\todo{Answer}

\begin{mdframed}[style=comment] 
The validation error might be slightly below the training error as it is used to select hyper-parameters.

- I don't understand this statement. It could be that there is accidentally more correlation in the validation set, but I'm not sure what you mean by "it is used to select hyper-parameters" or why that would explain why there is less error in the validation set. Can you think about this further (and perhaps check for the amount of information in that data set compared to the training set)?
\end{mdframed}
\todo{Answer}

\begin{mdframed}[style=comment] 
The data is generated for the present analysis is based on the fast approximate N-Body simulation code L-PICOLA [71].

- The first "is" is superfluous.
\end{mdframed}
\todo{Answer}

\begin{mdframed}[style=comment]

Finally, after all these little points, I just want to congratulate the authors again on a great paper. It was a pleasure reading it. I will be sure to be using this method in the near future!
\end{mdframed}
\todo{Final thanks + contact us?}

### 2018-12-07 rebuttal.tex

\todo{Thanks the reviewer}

\subsection{}
\begin{mdframed}[style=comment] 
One fairly significant concern I have is how convincing the application to other machine learning algorithms is. The authors compare deep sphere to a SVM classifier, in the case of distinguising from two cosmological models from density maps. This classification is obviously a simplification of what would be done in real comsological analyses, but is sufficient for the purpose of demonstration here. However, the metrics adopted do not clearly highlight the superiority of DeepSphere. The SVM takes pixel histograms or power spectrum densities (PSDs) of each input map. It is not surprising that DeepSphere outperforms them given that it takes the whole map as input. Histograms and PSDs are very restrictive compressions of the data - dropping a lot of spatial information. An SVM or even a standard fully connected neural network (NN) would perform a lot better. It is unclear how that would compare to DeepSphere. But I would certainly expect DeepSphere to be a lot easier to train and have many fewer parameters, which I think is the key advantage that needs to be highlighted here. This is analogous to comparing a standard convolutional NN to a standard fully-connected NN. With appropriate depth both will extract the same information and perform equally well. But of course the CNN has fewer parameters and is easier to train since its structure naturally extracts spatial information. One wouldn't compare the CNN to a SVM trained on pixel histograms or PSDs, since those would not have access to the same information. It would be more natural to compare the CNN and the NN trained on the same maps, and examine the number of parameters, the time and number of examples needed for training to achieve the same performance, etc. This would truly highlight how the structure of the NN is a key advantage.
\end{mdframed}

\todo{Assigned: @nati, @michael
General answer:
\begin{itemize}
  \item `An SVM or even a standard fully connected neural network (NN) would perform a lot better.'
  a) I think that SVM fails (I think this this an overfitting problem. This is the case at least for the noiseless case, TO CHECK) I was able to run SVM, it works, but the result is pretty bad. TODO: do a full experiment.
  b) NN is computationally not even possible, or it would have to be a very striped down version of the network... We can actually try...
  The input number of pixel for our order $1$ is $1024^2$ which severly limits the number of neurons that can be used in a fully connected architecture. For the first layer, we were only able to $128$ neurons before hitting an out of memory errors. In this setting, with an relative amount of noise of 0.5, we were unable to find regularization setting for the network such that it would actually classify the validation set. Note that all calssifiers performed well in this particular setting. Similar conclusion were observed with other setting, even when increasing the number of neurons for order $2$ and $4$.
  \item The reviewer is correct with respect of the number of parameters
\end{itemize}
We should probably add to comparing curves SVM and fully connected
}

@@

\subsection{}
\begin{mdframed}[style=comment] 
Page 4: "There is no known point set that achieves the analogue of uniform sampling in Euclidean space and allows exact and invertible discrete spherical harmonic decompositions of arbitrary but band-limited functions." This is ambigious. There exists multiple schemes for performing exact SHT on band-limited signals. Those sampling are more efficient than healpix - often in terms of number of pixels, and sometimes in terms of performance of the spherical harmonic transforms - and more accurate since the transform is exact (at least numerically - so typical errors are machine precision). Healpix transforms are only exact to 1e-7 when using iterative schemes, and that depends on Nside and lmax. Please clarify this paragraph. Obviously healpix is very advantageous for the pooling and other operations that take advantage of its hierarchical nature. This is well discussed in the paper - in particular how the fast graph algorithms could accomodate other sampling schemes.
\end{mdframed}

\todo{Assigned to: @all whoever can answer this question. I just do not know the answer.
\begin{mdframed}[style=manuscript] 
blabla
\end{mdframed}
}

@@

\todo{Assigned: @nati 
We added
\begin{mdframed}[style=manuscript] 
blabla
\end{mdframed}}

\subsection{}

\begin{mdframed}[style=comment] 
Figure 3: What was resolution used for those maps? Does the projection of the eigenvectors depend on the resolution and band-limit? 
\end{mdframed}

\todo{@nati
We were actually limited in resolution when computing the graph Fourier eigenvectors as diagonalizing the Laplacian matrix scales as $O(N_{pix}^3)$. Hence we used a resolution of $N_{side}=16$. The information has been added to the paper. We believe that, with the correct weighting scheme the graph eigenvectors may converge toward the spherical harmonics as the resolution increases. We also believe that the eigenvector associated with the lowest $\ell$ "converges first". }

\subsection{}
\begin{mdframed}[style=comment] 
Page 7: "That is much more efficient than filtering with spherical harmonics, even though HEALPix was de- signed as an iso-latitude sampling that has a fast spherical transform. That is especially true for smooth kernels which require a low polynomial degree K. Figure 4 compares the speed of low-pass filtering for Gaussian smoothing using the spherical harmonics and the graph-based method presented here. A naive implementation of our method is ten to twenty times faster for Nside = 2048, with K = 20 and K = 5, respectively, than using the spherical harmonic transform at lmax = 3Nside implemented by the highly optimized libsharp [38] library used by HEALPix." This is not so clear. Is the graph method also performing a Gaussian smoothing with the same characteristics? If so, what are those? How precise is the graph convolution approximating the true harmonic-space Gaussian convolution in this case? This is relevant since some approximations (for instance when analyzing cosmic microwave background data) require high-precision Gaussian smoothing. Finally, is lipsharp optimizing Gaussian smoothing in any way?
\end{mdframed}
\todo{Assigned: @nati,
Tocheck: @tomek, @michael
\begin{itemize}
  \item No here we only care about filter speed. 
  \item Filters do not have to be the same as they are learned anyway by the network.
  \item Replacing healpix filtering with graph filtering might be possible (suggested by Appendix C and fig 14), but is probably not usable when precision is required. It is left for futur work.
\end{itemize}
}
